\section{Data Collection Study}
We conducted a data collection study to gather IMU data while performing touches on a smartphone.
Our collected dataset consists of 6 smartphone sensors that were sampled while participants performed successive touches on the smartphones front side. 
%Here report: How and why is the data collection study designed as it is?
\subsection{Design}
We used a repeated-measures design with one independent variable: \textsc{phone}, which was counterbalanced using Latin Balanced squares. To total amount of conditions was: \textsc{phone} $ = 4$.
\subsection{Apparatus}
Our dataset was generated using four different sized smartphones on which participants had to perform a certain amount of touches (for further information see \cref{sec:tasks}).
Our used phone sizes range from $ 4^{\prime\prime} $ (S3) to $ 5.96^{\prime\prime} $ (N6). 
Using phones of these sizes we were able to cover the sizes of everyday smartphones, including some high-end devices and create a generalizable machine-learning model.
For more technical details about the used devices see \cref{tab:devices}.
\begin{table}[t]
	\centering
	\begin{tabularx}{1\textwidth}{Xrd{1.2}d{3.1}d{2.2}d{1.2}d{2.2}d{1.2}d{1.2}}%{Xrd{1.2}d{3.1}d{2.2}d{1.2}d{2.2}d{1.2}d{1.2}}
		\toprule
		\multicolumn{1}{l}{\multirow{3}{*}{\shortstack[c]{\textbf{Device}}}}&
		\multicolumn{1}{c}{\multirow{3}{*}{\shortstack[c]{\textbf{Release}}}}&    \multicolumn{1}{c}{\multirow{3}{*}{\shortstack[c]{\textbf{Display}\\ \textbf{Size (in)}}}}&
		\multicolumn{1}{c}{\multirow{3}{*}{\shortstack[c]{\textbf{Weight}\\ \textbf{(g)}}}} &
		\multicolumn{1}{c}{\multirow{3}{*}{\shortstack[c]{\textbf{Screen}\\ \textbf{Diagonal}\\ \textbf{(in)}}}} &
		\multicolumn{1}{c}{\multirow{3}{*}{\shortstack[c]{\textbf{Height}\\ \textbf{(cm)}}}} &
		\multicolumn{1}{c}{\multirow{3}{*}{\shortstack[c]{\textbf{Width}\\ \textbf{(cm)}}}} &
		\multicolumn{1}{c}{\multirow{3}{*}{\shortstack[c]{\textbf{Depth}}}} \\ 
		\\
		\\
		\midrule
		Samsung Galaxy S3 Mini  & 2012 & 4. & 113 &  4. & 12.16 & 6.3 & 0.99 \\
		Samsung Galaxy S4 & 2013 & 4.8 & 130 &  5. & 13.7 & 7.0 & 0.79 \\
		OnePlus One & 2014 & 5.46 & 162 & 5.46 & 15.29 & 7.59 & 0.89 \\
		Motorola Nexus 6 & 2014 & 5.96 & 184 & 6. & 15.93 & 8.3 & 1.01 \\ 
		\bottomrule
	\end{tabularx}%
	\caption[Smartphone data]{\small Data about the smartphones that were used in the study.}
	\label{tab:devices}
\end{table}

\subsection{Tasks}
\label{sec:tasks}
For our data collection study participants had to perform a series of touches on the smartphones' touchscreen. 
We aligned the crosses participants had to touch in a 16 $ \times $ 9 grid. 
In order to achieve a high variance across the whole screen, we randomized the positions of the crosses within all the cells.
There were a total of 3 repetitions, resulting in $ 16 \times 9 \times 3 = 432 $ touches on one device.

Between two touches our study participants had to perform a simple \textit{Fitts' Law task}. 
Here participants had to drag a filled rectangle into a dashed contour of a rectangle.
This task was mainly implemented to reset the participants grip to the bottom half of the device, because a previous shifted grip of the hand to the upper half of the phone influences the recorded sensor data when reaching for targets in the lower half and vice versa. 
\subsection{Procedure}
Report about the whole procedure.
\subsection{Participants}
Report about age, gender, and similar demographics.
